### 2022-02-14 documentos/generators.tex
Moved something to somewhere... goodnight...

\cpnote{Notas, no entiendo que es 3+3. Ceo qe no es suma de Klein tampoco 
por un aparente contraejemeplo: 
$3=\Sigma(0) = \Sigma(0+0) = \Sigma(0)+\Sigma(0) = 3+3 = ??$}
\cpnote{Este es un mapeo que depende de $k$, por lo que propondria ponerle
o un subindice o un superindice $(k)$. }
\cpnote{La simetría clasifica también al generador!! Quizá podemos quitar el miniapendice
que había escrito}
A reflection symmetry is identified for both PCE generators $\pceg$ and
the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map.
The symmetry for a PCE generator $\pceg$ is encoded in the 
$N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
is either symmetric or anti-symmetric under reflection of the 
indices in the $k$-th position in $\vec\alpha$ as
\begin{equation}
\Sigma: 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
\end{equation}
Indeed, any generator is a subspace containing half the elements of the full vector space.  
The map $\Sigma$ has the following properties
\begin{enumerate}
\item $\Sigma(\vec\alpha)+\Sigma(\vec\beta)=\vec\alpha+\vec\beta$.
\item $\Sigma(\vec\alpha)\neq\vec\alpha$
\end{enumerate}
From the first property, we now obtain
\begin{equation}
\vec\alpha=\Sigma(\vec\alpha)+\Sigma(\vec0)
\end{equation}
We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
$\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.

>>>>

\cpnote{Este es un mapeo que depende de $k$, por lo que propondria ponerle
o un subindice o un superindice $(k)$. }
\cpnote{La simetría clasifica también al generador!! Quizá podemos quitar el miniapendice
que había escrito}
A reflection symmetry is identified for both PCE generators $\pceg$ and
the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map.
The symmetry for a PCE generator $\pceg$ is encoded in the 
$N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
is either symmetric or anti-symmetric under reflection of the 
indices in the $k$-th position in $\vec\alpha$. Consider the map
\begin{equation}
% \Sigma: 
0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
\label{eq:Sigma}
\end{equation}
Indeed, any generator is a subspace containing half the elements of the full vector space.  
Map \eref{eq:Sigma} applied to the $k$-th qubit has the following properties
\begin{enumerate}
\item $\Sigma(\vec\alpha)\oplus \Sigma(\vec\beta)=\vec\alpha\oplus \vec\beta$.
\item $\Sigma(\vec\alpha)\neq\vec\alpha$
\end{enumerate}
From the first property, we now obtain
\begin{equation}
\vec\alpha=\Sigma(\vec\alpha) \oplus \Sigma(\vec0)
\end{equation}
We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
$\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.
